Leaf traits and size drive differences in above-ground biomass distribution among woody plant functional types

### 2016-02-01 manuscript.Rnw
table with sample sizes added back

<<results='asis'>>=

print(xtable(table_varpart_gam,
             caption="Explained variance in four plant biomass variables by plant height (H), plant functional type (PFT) and climate. Shown are $R^2$ estimated with generalized additive models (GAM), with four set of predictors. All variables except PFT were added as smooth terms to the GAMs, avoiding the need to assume linear partial responses to the predictor variables, or search for best-fitting transformations. Climate variables included were either MAT or aridity index (calculated as the of PET to MAP)."),sanitize.text.function=function(x){x},
      include.rownames=FALSE, caption.placement = "top")

>>>>

<<results='asis'>>=
print(xtable(table_samplesize,
             caption="Sample sizes used for the four studied whole-plant variables, by plant functional type. Numbers indicate individual plants, with number of unique species between parentheses. Sample sized differed between variables because not all included studied measured all variables ("),
      sanitize.text.function=function(x){x},
      include.rownames=TRUE, caption.placement = "top")
@

<<results='asis'>>=
names(table_varpart_gam)[1] <- ""
print(xtable(table_varpart_gam,
             caption="Explained variance in four plant biomass variables by plant height (H), plant functional type (PFT) and climate. Shown are $R^2$ estimated with generalized additive models (GAM), with four set of predictors. All variables except PFT were added as smooth terms to the GAMs, avoiding the need to assume linear partial responses to the predictor variables, or search for best-fitting transformations. Climate variables included were either MAT or aridity index (calculated as the of PET to MAP)."),sanitize.text.function=function(x){x},
      include.rownames=FALSE, caption.placement = "top")
